---
title: "Report for Selected Communities"
output: html_document
params:
  IDs: NA
  Lusts: NA
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(tidyverse)
library(leaflet)
library(here)
library(vroom)

# Selected Block Groups
blkGrps <- as.data.frame(params$IDs)
releases <- as.data.frame(params$Lusts)

```


# Report of Selected Communities with Open Releases
Generated: `r Sys.Date()` 
United States Environmental Protection Agency: Office of Research and Development

## Selected Block Groups (National Percentiles)
Statistics for the selected block groups are shown in the table below.
```{r NationalTable}
# The `params` object is available in the document.
nat <- blkGrps%>%
  select(ID,ACSTOTPOP,MINORPCT,LOWINCPCT,N_Releases,
                   N_P_LDPNT,N_P_DSLPM,N_P_CANCR,N_P_RESP,N_P_PTRAF,N_P_PWDIS,N_P_PNPL,
                   N_P_PRMP,N_P_PTSDF,N_P_OZONE,N_P_PM25)

datatable(nat, colnames = c("Block Group","Population","% Minority","% Low Income","# Active Releases",
          "Lead Paint","Diesel PM","Cancer","Air Toxics","Traffic","Discharge to Water","NPL Sites",
          "RMP Sites","TSDF Sites","O-Zone","PM 2.5"),extensions = 'FixedColumns',rownames = FALSE,
  options = list(
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 1)))%>%
  formatStyle('N_Releases',
    color = styleInterval(c(1,5), c('black', 'black', 'white')),
    backgroundColor = styleInterval(c(1,5), c('#d1c758', '#c48210', '#c22a0c')))%>%
  formatStyle(c("N_P_LDPNT","N_P_DSLPM","N_P_CANCR","N_P_RESP","N_P_PTRAF","N_P_PWDIS","N_P_PNPL",
                   "N_P_PRMP","N_P_PTSDF","N_P_OZONE","N_P_PM25"),
              color = styleInterval(c(50,80,95), c('black','black', 'black', 'white')),
    backgroundColor = styleInterval(c(50,80,95), c('#37a619','#d1c758', '#c48210', '#c22a0c')))%>%
  formatPercentage(c("MINORPCT","LOWINCPCT"), 0)
```

## Selected Block Groups (State Percentiles)
```{r StateTable}
state <- blkGrps%>%
  select(ID,ACSTOTPOP,MINORPCT,LOWINCPCT,N_Releases,
                   ST_P_LDPNT,ST_P_DSLPM,ST_P_CANCR,ST_P_RESP,ST_P_PTRAF,ST_P_PWDIS,ST_P_PNPL,
                   ST_P_PRMP,ST_P_PTSDF,ST_P_OZONE,ST_P_PM25)

datatable(state,colnames = c("Block Group","Population","% Minority","% Low Income","# Active Releases",
          "Lead Paint","Diesel PM","Cancer","Air Toxics","Traffic","Discharge to Water","NPL Sites",
          "RMP Sites","TSDF Sites","O-Zone","PM 2.5"),extensions = 'FixedColumns',rownames = FALSE,
  options = list(
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 1)))%>%
  formatStyle('N_Releases',
    color = styleInterval(c(1,5), c('black', 'black', 'white')),
    backgroundColor = styleInterval(c(1,5), c('#d1c758', '#c48210', '#c22a0c')))%>%
  formatStyle(c("ST_P_LDPNT","ST_P_DSLPM","ST_P_CANCR","ST_P_RESP","ST_P_PTRAF","ST_P_PWDIS","ST_P_PNPL",
                   "ST_P_PRMP","ST_P_PTSDF","ST_P_OZONE","ST_P_PM25"),
              color = styleInterval(c(50,80,95), c('black','black', 'black', 'white')),
    backgroundColor = styleInterval(c(50,80,95), c('#37a619','#d1c758', '#c48210', '#c22a0c')))%>%
  formatPercentage(c("MINORPCT","LOWINCPCT"), 0)
```


## Map of Block Groups
```{r leaflet}
# Map Releases

leaflet(blkGrps)%>%
  addProviderTiles(providers$Esri.WorldImagery)%>%
  addWMSTiles(
                "https://tigerweb.geo.census.gov/arcgis/services/Census2020/tigerWMS_Census2010/MapServer/WMSServer",
                layers = "Census_Block_Groups59805",
                options = WMSTileOptions(format = "image/png", transparent = TRUE),
                attribution = "U.S. Census Bureau - 2020 Tiger"
            )%>%
  addCircleMarkers(
    radius = 12,
                color = "#b52121",
                stroke = FALSE, fillOpacity = 0.5
  )

```

## Seleceted Releases
```{r releases}
datatable(releases,extensions = 'FixedColumns',rownames = FALSE,
  options = list(
    dom = 't',
    scrollX = TRUE,
    fixedColumns = list(leftColumns = 2),pageLength = 6)
  )
```


## Map of Releases


```{r releaseMap}
leaflet(releases)%>%
  addProviderTiles(providers$Esri.WorldImagery)%>%
  addCircleMarkers(
    radius = 6,
    color = "black",
    fillColor = "#b52121",
    stroke = TRUE,
    fillOpacity = 1,
    popup = ~paste0("<b>",Name,"</b><br>",
                   "Address: ", Address,"<br>",
                   "City: ",City,"<br>",
                   "LUST ID: ",LUST_ID,"<br>",
                   "Reported: ",Reported_Date)
  )
```

